---
title: "HC Assessment R Code"
author: "Claude Haneum Lee"
date: "12/17/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(dplyr)
library(stringr)
library(ggplot2)
library(grid)
library(gridExtra)
library(coin)
```

# Data Export

## Residence Info
```{r}
StarRez <- read_csv("Data 12-2-20/StarRez Data.csv", 
                    col_types = cols(Location = col_factor(levels = c("Shoemaker Hall", 
                                                                      "Mitchell Hall", 
                                                                      "Sherburne Hall", 
                                                                      "Stearns Hall", 
                                                                      "Case Hall", 
                                                                      "Hill Hall", 
                                                                      "Stateview North",
                                                                      "Stateview South",
                                                                      "Lawrence Hall")), 
                                     `Tech ID` = col_character()))
```


## CA Data

### Base Data

```{r}
CA <- read_csv("Data 12-2-20/HC Survey - CAs.csv", 
               col_names = FALSE, col_types = cols(X18 = col_character()), 
               skip = 3)
CA <- CA %>% 
  select(-c(1:6, 8:17))
names(CA) <- c("Finished", "StudentID", "LastName", "FirstName", "Hall1", "Floor", 
               "Sched", "SchedOther", "SchedNT", "SchedNTOther", 
               "Comm", "CommOther", "CommNT", "CommNTOther", "Meet", "MeetOther", "MeetNT", "MeetNTOther", 
               "Feedback", "FeedbackOther", "FeedbackReason", 
               "SC1", "SC2", "SC3", "SC4", "SC5", "CM1", "CM2", "CM3", "CM4", "CM5", "VC1", "VC2", "VC3", "VC4", "VC5")

#Check Student ID entry error
for (i in 1:nrow(CA)) {
  if ((CA$StudentID[i] %in% StarRez$'Tech ID') == FALSE) {print(CA[i,c(2:6)])}
}

#Remove Unfinished Response
o <- vector()
for (k in 1:nrow(CA)) {
  if (CA$Finished[k] == FALSE) {o <- append(o, k, length(o))}
}
CA <- CA[-o, ]

#Check Duplicate Entry
l <- as.data.frame(table(CA$StudentID))
for (j in 1:nrow(l)) {
  if (l[j,2] != 1) {print(l[j,])}
}

#Fluency Score Convert

for (i in (ncol(CA)-14):ncol(CA)) {
  a <- vector()
  for (j in 1:nrow(CA)) {
    if (is.na(CA[j, i])) {a[j] <- 0}
    else if (CA[j, i] == "Know how to use this feature") {a[j] <- 1}
    else if (CA[j, i] == "Use this feature frequently") {a[j] <- 2}
    else if (CA[j, i] == "Know how to use this feature,Use this feature frequently") {a[j] <- 2}
  }
  CA[i] <- a
}

#Change "Other ..." Entry
for (i in 1:ncol(CA)) {
  for (j in 1:nrow(CA)) {
    if (startsWith(toString(CA[j, i]), "Other") == TRUE) {
      CA[j, i] <- "Other"
    }
  }
}



#Join StarRez Data
CA2 <- inner_join(CA, StarRez, by = c("StudentID" = "Tech ID")) %>% 
  select(StudentID, Location, Floor, Sched:VC5) %>% 
  mutate(SCkn = (SC1 %in% c(1,2)) + (SC2 %in% c(1,2)) + (SC3 %in% c(1,2)) + (SC4 %in% c(1,2)) + (SC5 %in% c(1,2)), 
         SCus = (SC1 == 1) + (SC2 == 1) + (SC3 == 1) + (SC4 == 1) + (SC5 == 1), 
         CMkn = (CM1 %in% c(1,2)) + (CM2 %in% c(1,2)) + (CM3 %in% c(1,2)) + (CM4 %in% c(1,2)) + (CM5 %in% c(1,2)), 
         CMus = (CM1 == 1) + (CM2 == 1) + (CM3 == 1) + (CM4 == 1) + (CM5 == 1), 
         VCkn = (VC1 %in% c(1,2)) + (VC2 %in% c(1,2)) + (VC3 %in% c(1,2)) + (VC4 %in% c(1,2)) + (VC5 %in% c(1,2)), 
         VCus = (VC1 == 1) + (VC2 == 1) + (VC3 == 1) + (VC4 == 1) + (VC5 == 1))
```


### Clean Response

```{r}
#Group/Rename Halls
Hall <- vector()
for (i in 1:nrow(CA2)) {
  if (CA2$Location[i]== "Shoemaker Hall") {Hall[i] <- "Shoemaker"}
  else if (CA2$Location[i]== "Mitchell Hall") {Hall[i] <- "Mitchell"}
  else if (CA2$Location[i]== "Sherburne Hall") {Hall[i] <- "Sherburne"}
  else if (CA2$Location[i]== "Stearns Hall") {Hall[i] <- "Stearns"}
  else if (CA2$Location[i]%in% c("Case Hall", "Hill Hall")) {Hall[i] <- "Case-Hill"}
  else if (CA2$Location[i]%in% c("Stateview North", "Stateview South")) {Hall[i] <- "Stateview"}
}
CA2 <- as.data.frame(cbind(Hall, CA2))

# Sched
for (i in 1:nrow(CA2)) {
  if (CA2$Sched[i] == "Hand-written schedule") {CA2$Sched[i] <- "Hand-Written"}
  else if (startsWith(CA2$Sched[i], "Online")) {CA2$Sched[i] <- "Online App"}
}

# SchedNT
for (i in 1:nrow(CA2)) {
  if (is.na(CA2$SchedNT[i]) == FALSE) {
    if (startsWith(CA2$SchedNT[i],"Hand-written schedule")) {CA2$SchedNT[i] <- "Easy to keep up"}
    else if (startsWith(CA2$SchedNT[i],"I am not")) {CA2$SchedNT[i] <- "Not fluent in such technology"}
    else if (startsWith(CA2$SchedNT[i],"It is")) {CA2$SchedNT[i] <- "Privacy"}
  }
}

# Comm
for (i in 1:nrow(CA2)) {
  if (startsWith(CA2$Comm[i], "Phone")) {CA2$Comm[i] <- "Phone/PhoneApp"}
}

# CommNT
for (i in 1:nrow(CA2)) {
  if (is.na(CA2$CommNT[i]) == FALSE) {
    if (startsWith(CA2$CommNT[i],"It is")) {CA2$CommNT[i] <- "Easy to get ahold"}
    else if (startsWith(CA2$CommNT[i],"I prefer")) {CA2$CommNT[i] <- "In-person Connections"}
    else if (startsWith(CA2$CommNT[i],"I am")) {CA2$CommNT[i] <- "Not fluent in other methods"}
  }
}

# Meet
for (i in 1:nrow(CA2)) {
  if (startsWith(CA2$Meet[i], "Video")) {CA2$Meet[i] <- "Online App"}
  else if (startsWith(CA2$Meet[i], "Phone")) {CA2$Meet[i] <- "Phone/PhoneApp"}
  else if (startsWith(CA2$Meet[i], "I will")) {CA2$Meet[i] <- "Still in-person"}
}

# MeetNT
for (i in 1:nrow(CA2)) {
  if (is.na(CA2$MeetNT[i]) == FALSE) {
    if (startsWith(CA2$MeetNT[i],"Possible")) {CA2$MeetNT[i] <- "In-person Connections"}
    else if (startsWith(CA2$MeetNT[i],"Easier")) {CA2$MeetNT[i] <- "Easy to facilitate"}
    else if (startsWith(CA2$MeetNT[i],"I am")) {CA2$MeetNT[i] <- "Not fluent in other methods"}
  }
}
```


### Multiple Selection Data

```{r}
# Feedback
CAFeedback <- vector()
for (i in 1:nrow(CA2)) {
  CAFeedback<- append(CAFeedback, unlist(strsplit(CA2$Feedback[i], ",")), length(CAFeedback))
}
```



## Student Data

### Base Data

```{r}
Student <- read_csv("Data 12-2-20/HC Survey - Students.csv", 
               col_names = FALSE, col_types = cols(X18 = col_character()), 
               skip = 5)
Student <- Student %>% 
  select(-c(1:6, 8:17))
names(Student) <- c("Finished", "StudentID", "LastName", "FirstName", "Hall1", "Referral", 
               "SchedCA", "SchedCAApp", "SchedCAAppOther", "Sched", "SchedOther", "SchedNT", "SchedNTOther", 
               "CommCA", "CommCAOther", "CommCAApp", "CommCAAppOther", "Comm", "CommOther", "CommNT", "CommNTOther", 
               "MeetCA", "MeetCAOther", "MeetCAApp", "MeetCAAppOther", "Meet", "MeetOther", "MeetNT", "MeetNTOther", 
               "Feedback", "FeedbackOther", "FeedbackReason", 
               "SC1", "SC2", "SC3", "SC4", "SC5", "CM1", "CM2", "CM3", "CM4", "CM5", "VC1", "VC2", "VC3", "VC4", "VC5")


#Check Student ID entry error
for (i in 1:nrow(Student)) {
  if ((Student$StudentID[i] %in% StarRez$'Tech ID') == FALSE) {print(Student[i,c(2:6)])}
}

#Check CA entry in Student Survey and remove
c <- vector()
for (i in 1:nrow(Student)) {
  if ((Student$StudentID[i] %in% CA$'StudentID')) {
    c <- append(c, i, length(c))}
}
Student <- Student[-c,]

#Remove Unfinished Response
o <- vector()
for (k in 1:nrow(Student)) {
  if (Student$Finished[k] == FALSE) {o <- append(o, k, length(o))}
}
Student <- Student[-o, ]

#Check Duplicate Entry
l <- as.data.frame(table(Student$StudentID))
for (j in 1:nrow(l)) {
  if (l[j,2] != 1) {print(l[j,])}
}

#Fluency Score Convert
for (i in (ncol(Student)-14):ncol(Student)) {
  a <- vector()
  for (j in 1:nrow(Student)) {
    if (is.na(Student[j, i])) {a[j] <- 0}
    else if (Student[j, i] == "Know how to use this feature") {a[j] <- 1}
    else if (Student[j, i] == "Use this feature frequently") {a[j] <- 2}
    else if (Student[j, i] == "Know how to use this feature,Use this feature frequently") {a[j] <- 2}
  }
  Student[i] <- a
}

#Change "Other ..." Entry
for (i in 1:ncol(Student)) {
  for (j in 1:nrow(Student)) {
    if (startsWith(toString(Student[j, i]), "Other") == TRUE) {
      Student[j, i] <- "Other"
    }
  }
}

#Join StarRez Data
Student2 <- inner_join(Student, StarRez, by = c("StudentID" = "Tech ID")) %>% 
  select(StudentID, Location, Referral:VC5) %>% 
  mutate(SCkn = (SC1 %in% c(1,2)) + (SC2 %in% c(1,2)) + (SC3 %in% c(1,2)) + (SC4 %in% c(1,2)) + (SC5 %in% c(1,2)), 
         SCus = (SC1 == 1) + (SC2 == 1) + (SC3 == 1) + (SC4 == 1) + (SC5 == 1), 
         CMkn = (CM1 %in% c(1,2)) + (CM2 %in% c(1,2)) + (CM3 %in% c(1,2)) + (CM4 %in% c(1,2)) + (CM5 %in% c(1,2)), 
         CMus = (CM1 == 1) + (CM2 == 1) + (CM3 == 1) + (CM4 == 1) + (CM5 == 1), 
         VCkn = (VC1 %in% c(1,2)) + (VC2 %in% c(1,2)) + (VC3 %in% c(1,2)) + (VC4 %in% c(1,2)) + (VC5 %in% c(1,2)), 
         VCus = (VC1 == 1) + (VC2 == 1) + (VC3 == 1) + (VC4 == 1) + (VC5 == 1))
```


### Clean Response

```{r}
#Group/Rename Halls
Hall <- vector()
for (i in 1:nrow(Student2)) {
  if (Student2$Location[i]== "Shoemaker Hall") {Hall[i] <- "Shoemaker"}
  else if (Student2$Location[i]== "Mitchell Hall") {Hall[i] <- "Mitchell"}
  else if (Student2$Location[i]== "Sherburne Hall") {Hall[i] <- "Sherburne"}
  else if (Student2$Location[i]== "Stearns Hall") {Hall[i] <- "Stearns"}
  else if (Student2$Location[i]%in% c("Case Hall", "Hill Hall")) {Hall[i] <- "Case-Hill"}
  else if (Student2$Location[i]%in% c("Stateview North", "Stateview South")) {Hall[i] <- "Stateview"}
}
Student2 <- as.data.frame(cbind(Hall, Student2))

# Sched
for (i in 1:nrow(Student2)) {
  if (Student2$Sched[i] == "Hand-written schedule") {Student2$Sched[i] <- "Hand-Written"}
  else if (startsWith(Student2$Sched[i], "Online")) {Student2$Sched[i] <- "Online App"}
}

# SchedNT
for (i in 1:nrow(Student2)) {
  if (is.na(Student2$SchedNT[i]) == FALSE) {
    if (startsWith(Student2$SchedNT[i],"Hand-written schedule")) {Student2$SchedNT[i] <- "Easy to keep up"}
    else if (startsWith(Student2$SchedNT[i],"I am not")) {Student2$SchedNT[i] <- "Not fluent in such technology"}
    else if (startsWith(Student2$SchedNT[i],"It is")) {Student2$SchedNT[i] <- "Privacy"}
  }
}

# Comm
for (i in 1:nrow(Student2)) {
  if (startsWith(Student2$Comm[i], "Phone")) {Student2$Comm[i] <- "Phone/PhoneApp"}
}

# CommNT
for (i in 1:nrow(Student2)) {
  if (is.na(Student2$CommNT[i]) == FALSE) {
    if (startsWith(Student2$CommNT[i],"It is")) {Student2$CommNT[i] <- "Easy to get ahold"}
    else if (startsWith(Student2$CommNT[i],"I prefer")) {Student2$CommNT[i] <- "In-person Connections"}
    else if (startsWith(Student2$CommNT[i],"I am")) {Student2$CommNT[i] <- "Not fluent in other methods"}
  }
}

# MeetCA
for (i in 1:nrow(Student2)) {
  if (startsWith(Student2$MeetCA[i], "Video")) {Student2$MeetCA[i] <- "Online App"}
  else if (startsWith(Student2$MeetCA[i], "Phone")) {Student2$MeetCA[i] <- "Phone/PhoneApp"}
  else if (startsWith(Student2$MeetCA[i], "In-")) {Student2$MeetCA[i] <- "In-Person"}
}

# Meet
for (i in 1:nrow(Student2)) {
  if (startsWith(Student2$Meet[i], "Video")) {Student2$Meet[i] <- "Online App"}
  else if (startsWith(Student2$Meet[i], "Phone")) {Student2$Meet[i] <- "Phone/PhoneApp"}
  else if (startsWith(Student2$Meet[i], "I will")) {Student2$Meet[i] <- "Still in-person"}
}

# MeetNT
for (i in 1:nrow(Student2)) {
  if (is.na(Student2$MeetNT[i]) == FALSE) {
    if (startsWith(Student2$MeetNT[i],"Possible")) {Student2$MeetNT[i] <- "In-person Connections"}
    else if (startsWith(Student2$MeetNT[i],"Easier")) {Student2$MeetNT[i] <- "Easy to be part of"}
    else if (startsWith(Student2$MeetNT[i],"I am")) {Student2$MeetNT[i] <- "Not fluent in other methods"}
  }
}
```


### Multiple Selection Data

```{r}
# SchedCAApp
StudentSchedCAApp <- vector()
for (i in 1:nrow(Student2)) {
  if (is.na(Student2$SchedCAApp[i]) == FALSE) {
    StudentSchedCAApp <- append(StudentSchedCAApp, unlist(strsplit(Student2$SchedCAApp[i], ",")), length(StudentSchedCAApp))
  }
}
for (i in 1:length(StudentSchedCAApp)) {
  if (startsWith(StudentSchedCAApp[i], "Other") == TRUE) {StudentSchedCAApp[i] <- "Other"}
  else if (startsWith(StudentSchedCAApp[i], "Outlook") == TRUE) {StudentSchedCAApp[i] <- "Outlook"}
}

# CommCAApp
StudentCommCAApp <- vector()
for (i in 1:nrow(Student2)) {
  if (is.na(Student2$CommCAApp[i]) == FALSE) {
    StudentCommCAApp <- append(StudentCommCAApp, unlist(strsplit(Student2$CommCAApp[i], ",")), length(StudentCommCAApp))
  }
}
for (i in 1:length(StudentCommCAApp)) {
  if (startsWith(StudentCommCAApp[i], "Other") == TRUE) {StudentCommCAApp[i] <- "Other"}
  else if (startsWith(StudentCommCAApp[i], "Phone") == TRUE) {StudentCommCAApp[i] <- "Phone"}
  else if (startsWith(StudentCommCAApp[i], "Outlook") == TRUE) {StudentCommCAApp[i] <- "Outlook"}
}

# MeetCAApp
StudentMeetCAApp <- vector()
for (i in 1:nrow(Student2)) {
  if (is.na(Student2$MeetCAApp[i]) == FALSE) {
    StudentMeetCAApp <- append(StudentMeetCAApp, unlist(strsplit(Student2$MeetCAApp[i], ",")), length(StudentMeetCAApp))
  }
}
for (i in 1:length(StudentMeetCAApp)) {
  if (startsWith(StudentMeetCAApp[i], "Other") == TRUE) {StudentMeetCAApp[i] <- "Other"}
  else if (startsWith(StudentMeetCAApp[i], "Phone") == TRUE) {StudentMeetCAApp[i] <- "Phone"}
  else if (startsWith(StudentMeetCAApp[i], "Outlook") == TRUE) {StudentMeetCAApp[i] <- "Outlook"}
}

# Feedback
StudentFeedback <- vector()
for (i in 1:nrow(Student2)) {
  StudentFeedback<- append(StudentFeedback, unlist(strsplit(Student2$Feedback[i], ",")), length(StudentFeedback))
}
```


### Student Data Student ID List

```{r eval=FALSE, include=FALSE}
cat(Student2$StudentID, sep = "\n")
```


### Join Demographic Data

```{r}
library(readxl)
library(eeptools)
Dem <- read_excel("Data 12-2-20/HC Demographic Data.xlsx", 
                  col_types = c("text", "text", "date", "text", "text", "text"))
Dem$Class <- factor(Dem$Class,levels = c("FR", "SO", "JR", "SR"))
Dem <- mutate(Dem, Age = floor(age_calc(as.Date(Dem$DOB), unit = "years")))
Student2 <- inner_join(Student2, Dem, by = c("StudentID" = "StudentID"))
```






# Use of Technology 

## Completion by Hall

```{r}
library(tidyverse)
# CA
p <- ggplot(CA2, aes(x = Location)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 15), 
        axis.title.x = element_blank())
k <- tableGrob(unname(as.data.frame(table(CA2$Location))), rows = NULL)  
grid.arrange(p, k, ncol=2, widths = c(3, 1), top = textGrob("CA Completion Count", gp = gpar(fontsize = 30)))

# Student
m <- as.data.frame(cbind(round(table(Student2$Location)/table(StarRez$Location) * 100, 2), table(Student2$Location), round(table(StarRez$Location)*0.2)))
names(m) <- c("Prop", "Count", "Goal")
m <- m %>% 
  arrange(desc(Prop))
k <- tableGrob(m)  
grid.arrange(k, top = textGrob("Student Completion", gp = gpar(fontsize = 30)))
```


## Scheduling 

### Scheduling Method Preference

```{r}
# a. CA Preference
ggplot(CA2, aes(x = Sched)) +
  geom_bar() +
  geom_text(stat='count', aes(label=..count..), vjust=1, size = 8, color = "blue") +
  labs(title = "CA Scheduling Preference") +
  theme(plot.title = element_text(hjust = 0.5, size = 20), 
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))

# b. Student Experience from CA
ggplot(Student2, aes(x = SchedCA)) +
  geom_bar() +
  geom_text(stat='count', aes(label=..count..), vjust=1, size = 8, color = "blue") +
  labs(title = "Has your CA use any online app to schedule an event with you?") +
  theme(plot.title = element_text(hjust = 0.5, size = 17), 
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))

# c. Student Preference
ggplot(Student2, aes(x = Sched)) +
  geom_bar() +
  geom_text(stat='count', aes(label=..count..), vjust=1, size = 8, color = "blue") +
  labs(title = "Student Scheduling Preference") +
  theme(plot.title = element_text(hjust = 0.5, size = 20), 
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))
```


### Online Scheduling App

```{r}
ggplot(as.data.frame(StudentSchedCAApp), aes(x = StudentSchedCAApp)) +
  geom_bar() +
  geom_text(stat='count', aes(label=..count..), vjust=1, size = 8, color = "blue") +
  labs(title = "What online app did your CA use to schedule an event with you?") +
  theme(plot.title = element_text(hjust = 0.5, size = 17), 
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))
```


### Hand-Written Scheduling Reason

```{r}
# a. CA Reason
ggplot(drop_na(CA2, SchedNT), aes(x = SchedNT)) +
  geom_bar() +
  geom_text(stat='count', aes(label=..count..), vjust=1, size = 8, color = "blue") +
  labs(title = "CA Why Hand-Written Schedule?") +
  theme(plot.title = element_text(hjust = 0.5, size = 20), 
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 12))

# b. Student Reason
ggplot(drop_na(Student2, SchedNT), aes(x = SchedNT)) +
  geom_bar() +
  geom_text(stat='count', aes(label=..count..), vjust=1, size = 8, color = "blue") +
  labs(title = "Student Why Hand-Written Schedule?") +
  theme(plot.title = element_text(hjust = 0.5, size = 20), 
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 12))
```


## Communication

### Communication Method Preference

```{r}
# a. CA Preference
ggplot(CA2, aes(x = Comm)) +
  geom_bar() +
  geom_text(stat='count', aes(label=..count..), vjust=1, size = 8, color = "blue") +
  labs(title = "CA Communication Preference") +
  theme(plot.title = element_text(hjust = 0.5, size = 20), 
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))

# b. Student Experience from CA
ggplot(Student2, aes(x = CommCA)) +
  geom_bar() +
  geom_text(stat='count', aes(label=..count..), vjust=1, size = 8, color = "blue") +
  labs(title = "What method does your CA primarily use to contact you?") +
  theme(plot.title = element_text(hjust = 0.5, size = 17), 
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))

# c. Student Preference
ggplot(Student2, aes(x = Comm)) +
  geom_bar() +
  geom_text(stat='count', aes(label=..count..), vjust=1, size = 8, color = "blue") +
  labs(title = "Student Communication Preference") +
  theme(plot.title = element_text(hjust = 0.5, size = 20), 
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))
```


### Online Communication App

```{r}
ggplot(as.data.frame(StudentCommCAApp), aes(x = StudentCommCAApp)) +
  geom_bar() +
  geom_text(stat='count', aes(label=..count..), vjust=1, size = 8, color = "blue") +
  labs(title = "What online app did your CA use to communicate with you?") +
  theme(plot.title = element_text(hjust = 0.5, size = 17),
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))
```


### In-Person Communication Reason

```{r}
# a. CA Reason
ggplot(drop_na(CA2, CommNT), aes(x = CommNT)) +
  geom_bar() +
  geom_text(stat='count', aes(label=..count..), vjust=1, size = 8, color = "blue") +
  labs(title = "CA Why in-person communication?") +
  theme(plot.title = element_text(hjust = 0.5, size = 20), 
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))

# b. Student Reason
ggplot(drop_na(Student2, CommNT), aes(x = CommNT)) +
  geom_bar() +
  geom_text(stat='count', aes(label=..count..), vjust=1, size = 8, color = "blue") +
  labs(title = "Student Why in-person communication?") +
  theme(plot.title = element_text(hjust = 0.5, size = 20), 
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))
```


## Meeting

### Meeting Method Preference

```{r}
# a. CA Preference
ggplot(CA2, aes(x = Meet)) +
  geom_bar() +
  geom_text(stat='count', aes(label=..count..), vjust=1, size = 8, color = "blue") +
  labs(title = "CA Meeting Preference") +
  theme(plot.title = element_text(hjust = 0.5, size = 20), 
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))

# b. Student Experience from CA
ggplot(Student2, aes(x = MeetCA)) +
  geom_bar() +
  geom_text(stat='count', aes(label=..count..), vjust=1, size = 8, color = "blue") +
  labs(title = "Which method did your CA used in meeting with you?") +
  theme(plot.title = element_text(hjust = 0.5, size = 18), 
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))

# c. Student Preference
ggplot(Student2, aes(x = Meet)) +
  geom_bar() +
  geom_text(stat='count', aes(label=..count..), vjust=1, size = 8, color = "blue") +
  labs(title = "Student Meeting Preference") +
  theme(plot.title = element_text(hjust = 0.5, size = 20), 
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))
```


### Online Meeting App

```{r}
ggplot(as.data.frame(StudentMeetCAApp), aes(x = StudentMeetCAApp)) +
  geom_bar() +
  geom_text(stat='count', aes(label=..count..), vjust=1, size = 8, color = "blue") +
  labs(title = "What online app did your CA use to facilitate meetings with you?") +
  theme(plot.title = element_text(hjust = 0.5, size = 17),
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 12))
```


### In-Person Reason

```{r}
# a. CA Reason
ggplot(drop_na(CA2, MeetNT), aes(x = MeetNT)) +
  geom_bar() +
  geom_text(stat='count', aes(label=..count..), vjust=1, size = 8, color = "blue") +
  labs(title = "CA Why in-person meeting?") +
  theme(plot.title = element_text(hjust = 0.5, size = 20), 
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))

# b. Student Reason
ggplot(drop_na(Student2, MeetNT), aes(x = MeetNT)) +
  geom_bar() +
  geom_text(stat='count', aes(label=..count..), vjust=1, size = 8, color = "blue") +
  labs(title = "Student Why in-person meeting?") +
  theme(plot.title = element_text(hjust = 0.5, size = 20), 
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))
```


## Technology Area Feedback

```{r}
# a. CA Feedback
ggplot(as.data.frame(CAFeedback), aes(x = CAFeedback)) +
  geom_bar() +
  geom_text(stat='count', aes(label=..count..), vjust=1, size = 8, color = "blue") +
  labs(title = "CA Which areas in Res Life need more use of technology?") +
  theme(plot.title = element_text(hjust = 0.5, size = 17), 
        axis.title.x = element_blank(), 
        axis.text.x = element_text(angle = 15, size = 15),
        axis.text.y = element_text(size = 12))

# b. Student Reason
ggplot(as.data.frame(StudentFeedback), aes(x = StudentFeedback)) +
  geom_bar() +
  geom_text(stat='count', aes(label=..count..), vjust=1, size = 8, color = "blue") +
  labs(title = "Student CA Which areas in Res Life need more use of technology?") +
  theme(plot.title = element_text(hjust = 0.5, size = 17), 
        axis.title.x = element_blank(), 
        axis.text.x = element_text(angle = 15, size = 15),
        axis.text.y = element_text(size = 12))
```

# Technology Fluency & Usage

## Fluency vs Usage

```{r}
#Scheduling
t.test(Student2$SCkn, Student2$SCus, paired = TRUE, alternative = "greater")

#Communication
t.test(Student2$CMkn, Student2$CMus, paired = TRUE, alternative = "greater")

#Meeting
t.test(Student2$VCkn, Student2$VCus, paired = TRUE, alternative = "greater")
```


## Three Scores

### Fluency

```{r}
mean(Student2$SCkn)
mean(Student2$CMkn)
mean(Student2$VCkn)

#Scheduling vs Communication
t.test(Student2$SCkn, Student2$CMkn, paired = TRUE)

#Scheduling vs Meeting
t.test(Student2$SCkn, Student2$VCkn, paired = TRUE)

#Communication vs Meeting
t.test(Student2$CMkn, Student2$VCkn, paired = TRUE)
```

### Usage

```{r}
mean(Student2$SCus)
mean(Student2$CMus)
mean(Student2$VCus)

#Scheduling vs Communication
t.test(Student2$SCus, Student2$CMus, paired = TRUE)

#Scheduling vs Meeting
t.test(Student2$SCus, Student2$VCus, paired = TRUE)

#Communication vs Meeting
t.test(Student2$CMus, Student2$VCus, paired = TRUE)
```


## CA vs Students

### Fluency

```{r}
#Scheduling
SCkn <- data.frame(score <- c(CA2$SCkn, Student2$SCkn),
                   group <- c(rep("CA", nrow(CA2)), rep("Student", nrow(Student2))))
ggplot(SCkn, aes(x = group, y = score, color = group)) +
  geom_point(position = "jitter", show.legend = FALSE) +
  geom_hline(yintercept = mean(CA2$SCkn), color = "pink") +
  geom_hline(yintercept = mean(Student2$SCkn), color = "skyblue") +
  labs(title = "Scheduling Technology Fluency") +
  theme(plot.title = element_text(hjust = 0.5, size = 20), 
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))

t.test(score ~ group, data = SCkn, alternative = "greater")
mean(CA2$SCkn) - mean(Student2$SCkn)

#Communication
CMkn <- data.frame(score <- c(CA2$CMkn, Student2$CMkn),
                   group <- c(rep("CA", nrow(CA2)), rep("Student", nrow(Student2))))
ggplot(CMkn, aes(x = group, y = score, color = group)) +
  geom_point(position = "jitter", show.legend = FALSE) +
  geom_hline(yintercept = mean(CA2$CMkn), color = "pink") +
  geom_hline(yintercept = mean(Student2$CMkn), color = "skyblue") +
  labs(title = "Communication Technology Fluency") +
  theme(plot.title = element_text(hjust = 0.5, size = 20), 
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))

t.test(score ~ group, data = CMkn, alternative = "greater")
mean(CA2$CMkn) - mean(Student2$CMkn)

#Meeting
VCkn <- data.frame(score <- c(CA2$VCkn, Student2$VCkn),
                   group <- c(rep("CA", nrow(CA2)), rep("Student", nrow(Student2))))
ggplot(VCkn, aes(x = group, y = score, color = group)) +
  geom_point(position = "jitter", show.legend = FALSE) +
  geom_hline(yintercept = mean(CA2$VCkn), color = "pink") +
  geom_hline(yintercept = mean(Student2$VCkn), color = "skyblue") +
  labs(title = "Meeting Technology Fluency") +
  theme(plot.title = element_text(hjust = 0.5, size = 20), 
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))

t.test(score ~ group, data = VCkn, alternative = "greater")
mean(CA2$VCkn) - mean(Student2$VCkn)
```


### Usage

```{r}
#Scheduling
SCus <- data.frame(score <- c(CA2$SCus, Student2$SCus),
                   group <- c(rep("CA", nrow(CA2)), rep("Student", nrow(Student2))))
ggplot(SCus, aes(x = group, y = score, color = group)) +
  geom_point(position = "jitter", show.legend = FALSE) +
  geom_hline(yintercept = mean(CA2$SCus), color = "#F8766D") +
  geom_hline(yintercept = mean(Student2$SCus), color = "#00BFC4") +
  labs(title = "Scheduling Technology Usage") +
  theme(plot.title = element_text(hjust = 0.5, size = 20), 
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))

t.test(score ~ group, data = SCus, alternative = "less")
mean(CA2$SCus) - mean(Student2$SCus)

#Communication
CMus <- data.frame(score <- c(CA2$CMus, Student2$CMus),
                   group <- c(rep("CA", nrow(CA2)), rep("Student", nrow(Student2))))
ggplot(CMus, aes(x = group, y = score, color = group)) +
  geom_point(position = "jitter", show.legend = FALSE) +
  geom_hline(yintercept = mean(CA2$CMus), color = "#F8766D") +
  geom_hline(yintercept = mean(Student2$CMus), color = "#00BFC4") +
  labs(title = "Communication Technology Usage") +
  theme(plot.title = element_text(hjust = 0.5, size = 20), 
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))

t.test(score ~ group, data = CMus, alternative = "greater")
mean(CA2$CMus) - mean(Student2$CMus)

#Meeting
VCus <- data.frame(score <- c(CA2$VCus, Student2$VCus),
                   group <- c(rep("CA", nrow(CA2)), rep("Student", nrow(Student2))))
ggplot(VCus, aes(x = group, y = score, color = group)) +
  geom_point(position = "jitter", show.legend = FALSE) +
  geom_hline(yintercept = mean(CA2$VCus), color = "#F8766D") +
  geom_hline(yintercept = mean(Student2$VCus), color = "#00BFC4") +
  labs(title = "Meeting Technology Usage") +
  theme(plot.title = element_text(hjust = 0.5, size = 20), 
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))

t.test(score ~ group, data = VCus, alternative = "less")
mean(CA2$VCus) - mean(Student2$VCus)
```


## Hall/Community

### Fluency
```{r}
#Scheduling
SCkn <- data.frame(score = Student2$SCkn,
                   group = as.factor(Student2$Hall))
ggplot(SCkn, aes(x = group, y = score, color = group)) +
  geom_point(position = "jitter", show.legend = FALSE) +
  geom_hline(yintercept = mean(filter(Student2, Hall == "Shoemaker")$SCkn), color = "#F8766D") +
  geom_hline(yintercept = mean(filter(Student2, Hall == "Mitchell")$SCkn), color = "#B79F00") +
  geom_hline(yintercept = mean(filter(Student2, Hall == "Sherburne")$SCkn), color = "#00BA38") +
  geom_hline(yintercept = mean(filter(Student2, Hall == "Stearns")$SCkn), color = "#00BFC4") +
  geom_hline(yintercept = mean(filter(Student2, Hall == "Case-Hill")$SCkn), color = "#619CFF") +
  geom_hline(yintercept = mean(filter(Student2, Hall == "Stateview")$SCkn), color = "#F564E3") +
  labs(title = "Scheduling Technology Fluency") +
  theme(plot.title = element_text(hjust = 0.5, size = 20), 
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))

meanSCkn <- data.frame(Mean = c(mean(filter(Student2, Hall == "Shoemaker")$SCkn),
                                 mean(filter(Student2, Hall == "Mitchell")$SCkn),
                                 mean(filter(Student2, Hall == "Sherburne")$SCkn),
                                 mean(filter(Student2, Hall == "Stearns")$SCkn),
                                 mean(filter(Student2, Hall == "Case-Hill")$SCkn),
                                 mean(filter(Student2, Hall == "Stateview")$SCkn)),
                       Hall = c("Shoemaker", "Mitchell", "Sherburne", "Stearns", "Case-Hill", "Stateview")) %>% 
  arrange(Mean)
meanSCkn
kruskal_test(score ~ group, data = SCkn, distribution = approximate())


#Communication
CMkn <- data.frame(score <- Student2$CMkn,
                   group <- as.factor(Student2$Hall))
ggplot(CMkn, aes(x = group, y = score, color = group)) +
  geom_point(position = "jitter", show.legend = FALSE) +
  geom_hline(yintercept = mean(filter(Student2, Hall == "Shoemaker")$CMkn), color = "#F8766D") +
  geom_hline(yintercept = mean(filter(Student2, Hall == "Mitchell")$CMkn), color = "#B79F00") +
  geom_hline(yintercept = mean(filter(Student2, Hall == "Sherburne")$CMkn), color = "#00BA38") +
  geom_hline(yintercept = mean(filter(Student2, Hall == "Stearns")$CMkn), color = "#00BFC4") +
  geom_hline(yintercept = mean(filter(Student2, Hall == "Case-Hill")$CMkn), color = "#619CFF") +
  geom_hline(yintercept = mean(filter(Student2, Hall == "Stateview")$CMkn), color = "#F564E3") +
  labs(title = "Communication Technology Fluency") +
  theme(plot.title = element_text(hjust = 0.5, size = 20), 
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))

meanCMkn <- data.frame(Mean = c(mean(filter(Student2, Hall == "Shoemaker")$CMkn),
                                 mean(filter(Student2, Hall == "Mitchell")$CMkn),
                                 mean(filter(Student2, Hall == "Sherburne")$CMkn),
                                 mean(filter(Student2, Hall == "Stearns")$CMkn),
                                 mean(filter(Student2, Hall == "Case-Hill")$CMkn),
                                 mean(filter(Student2, Hall == "Stateview")$CMkn)),
                       Hall = c("Shoemaker", "Mitchell", "Sherburne", "Stearns", "Case-Hill", "Stateview")) %>% 
  arrange(Mean)
meanCMkn
kruskal_test(score ~ group, data = CMkn, distribution = approximate())

#Meeting
VCkn <- data.frame(score <- Student2$VCkn,
                   group <- as.factor(Student2$Hall))
ggplot(VCkn, aes(x = group, y = score, color = group)) +
  geom_point(position = "jitter", show.legend = FALSE) +
  geom_hline(yintercept = mean(filter(Student2, Hall == "Shoemaker")$VCkn), color = "#F8766D") +
  geom_hline(yintercept = mean(filter(Student2, Hall == "Mitchell")$VCkn), color = "#B79F00") +
  geom_hline(yintercept = mean(filter(Student2, Hall == "Sherburne")$VCkn), color = "#00BA38") +
  geom_hline(yintercept = mean(filter(Student2, Hall == "Stearns")$VCkn), color = "#00BFC4") +
  geom_hline(yintercept = mean(filter(Student2, Hall == "Case-Hill")$VCkn), color = "#619CFF") +
  geom_hline(yintercept = mean(filter(Student2, Hall == "Stateview")$VCkn), color = "#F564E3") +
  labs(title = "Meeting Technology Fluency") +
  theme(plot.title = element_text(hjust = 0.5, size = 20), 
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))

meanVCkn <- data.frame(Mean = c(mean(filter(Student2, Hall == "Shoemaker")$VCkn),
                                 mean(filter(Student2, Hall == "Mitchell")$VCkn),
                                 mean(filter(Student2, Hall == "Sherburne")$VCkn),
                                 mean(filter(Student2, Hall == "Stearns")$VCkn),
                                 mean(filter(Student2, Hall == "Case-Hill")$VCkn),
                                 mean(filter(Student2, Hall == "Stateview")$VCkn)),
                       Hall = c("Shoemaker", "Mitchell", "Sherburne", "Stearns", "Case-Hill", "Stateview")) %>% 
  arrange(Mean)
meanVCkn
kruskal_test(score ~ group, data = VCkn, distribution = approximate())
```

### Usage
```{r}
#Scheduling
SCus <- data.frame(score = Student2$SCus,
                   group = as.factor(Student2$Hall))
ggplot(SCus, aes(x = group, y = score, color = group)) +
  geom_point(position = "jitter", show.legend = FALSE) +
  geom_hline(yintercept = mean(filter(Student2, Hall == "Shoemaker")$SCus), color = "#F8766D") +
  geom_hline(yintercept = mean(filter(Student2, Hall == "Mitchell")$SCus), color = "#B79F00") +
  geom_hline(yintercept = mean(filter(Student2, Hall == "Sherburne")$SCus), color = "#00BA38") +
  geom_hline(yintercept = mean(filter(Student2, Hall == "Stearns")$SCus), color = "#00BFC4") +
  geom_hline(yintercept = mean(filter(Student2, Hall == "Case-Hill")$SCus), color = "#619CFF") +
  geom_hline(yintercept = mean(filter(Student2, Hall == "Stateview")$SCus), color = "#F564E3") +
  labs(title = "Scheduling Technology Usage") +
  theme(plot.title = element_text(hjust = 0.5, size = 20), 
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))

meanSCus <- data.frame(Mean = c(mean(filter(Student2, Hall == "Shoemaker")$SCus),
                                 mean(filter(Student2, Hall == "Mitchell")$SCus),
                                 mean(filter(Student2, Hall == "Sherburne")$SCus),
                                 mean(filter(Student2, Hall == "Stearns")$SCus),
                                 mean(filter(Student2, Hall == "Case-Hill")$SCus),
                                 mean(filter(Student2, Hall == "Stateview")$SCus)),
                       Hall = c("Shoemaker", "Mitchell", "Sherburne", "Stearns", "Case-Hill", "Stateview")) %>% 
  arrange(Mean)
meanSCus
kruskal_test(score ~ group, data = SCus, distribution = approximate())


#Communication
CMus <- data.frame(score <- Student2$CMus,
                   group <- as.factor(Student2$Hall))
ggplot(CMus, aes(x = group, y = score, color = group)) +
  geom_point(position = "jitter", show.legend = FALSE) +
  geom_hline(yintercept = mean(filter(Student2, Hall == "Shoemaker")$CMus), color = "#F8766D") +
  geom_hline(yintercept = mean(filter(Student2, Hall == "Mitchell")$CMus), color = "#B79F00") +
  geom_hline(yintercept = mean(filter(Student2, Hall == "Sherburne")$CMus), color = "#00BA38") +
  geom_hline(yintercept = mean(filter(Student2, Hall == "Stearns")$CMus), color = "#00BFC4") +
  geom_hline(yintercept = mean(filter(Student2, Hall == "Case-Hill")$CMus), color = "#619CFF") +
  geom_hline(yintercept = mean(filter(Student2, Hall == "Stateview")$CMus), color = "#F564E3") +
  labs(title = "Communication Technology Usage") +
  theme(plot.title = element_text(hjust = 0.5, size = 20), 
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))

meanCMus <- data.frame(Mean = c(mean(filter(Student2, Hall == "Shoemaker")$CMus),
                                 mean(filter(Student2, Hall == "Mitchell")$CMus),
                                 mean(filter(Student2, Hall == "Sherburne")$CMus),
                                 mean(filter(Student2, Hall == "Stearns")$CMus),
                                 mean(filter(Student2, Hall == "Case-Hill")$CMus),
                                 mean(filter(Student2, Hall == "Stateview")$CMus)),
                       Hall = c("Shoemaker", "Mitchell", "Sherburne", "Stearns", "Case-Hill", "Stateview")) %>% 
  arrange(Mean)
meanCMus
kruskal_test(score ~ group, data = CMus, distribution = approximate())

#Meeting
VCus <- data.frame(score <- Student2$VCus,
                   group <- as.factor(Student2$Hall))
ggplot(VCus, aes(x = group, y = score, color = group)) +
  geom_point(position = "jitter", show.legend = FALSE) +
  geom_hline(yintercept = mean(filter(Student2, Hall == "Shoemaker")$VCus), color = "#F8766D") +
  geom_hline(yintercept = mean(filter(Student2, Hall == "Mitchell")$VCus), color = "#B79F00") +
  geom_hline(yintercept = mean(filter(Student2, Hall == "Sherburne")$VCus), color = "#00BA38") +
  geom_hline(yintercept = mean(filter(Student2, Hall == "Stearns")$VCus), color = "#00BFC4") +
  geom_hline(yintercept = mean(filter(Student2, Hall == "Case-Hill")$VCus), color = "#619CFF") +
  geom_hline(yintercept = mean(filter(Student2, Hall == "Stateview")$VCus), color = "#F564E3") +
  labs(title = "Meeting Technology Usage") +
  theme(plot.title = element_text(hjust = 0.5, size = 20), 
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))

meanVCus <- data.frame(Mean = c(mean(filter(Student2, Hall == "Shoemaker")$VCus),
                                 mean(filter(Student2, Hall == "Mitchell")$VCus),
                                 mean(filter(Student2, Hall == "Sherburne")$VCus),
                                 mean(filter(Student2, Hall == "Stearns")$VCus),
                                 mean(filter(Student2, Hall == "Case-Hill")$VCus),
                                 mean(filter(Student2, Hall == "Stateview")$VCus)),
                       Hall = c("Shoemaker", "Mitchell", "Sherburne", "Stearns", "Case-Hill", "Stateview")) %>% 
  arrange(Mean)
meanVCus
kruskal_test(score ~ group, data = VCus, distribution = approximate())
```


## Gender

```{r}
table(Student2$Gender)

#Since there is only one unknown, let's only focus on Male and Female
#Remove Unknown
Student3 <- filter(Student2, Gender != "Unknown")
```


### Fluency

```{r}
#Scheduling
SCkn <- data.frame(score = Student3$SCkn,
                   gender = as.factor(Student3$Gender))
ggplot(SCkn, aes(x = gender, y = score, color = gender)) +
  geom_point(position = "jitter", show.legend = FALSE) +
  geom_hline(yintercept = mean(filter(Student2, Gender == "Female")$SCkn), color = "#F8766D") +
  geom_hline(yintercept = mean(filter(Student2, Gender == "Male")$SCkn), color = "#00BFC4") +
  labs(title = "Scheduling Technology Fluency") +
  theme(plot.title = element_text(hjust = 0.5, size = 20), 
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))

t.test(score ~ gender, data = SCkn)
mean(filter(Student2, Gender == "Female")$SCkn) - mean(filter(Student2, Gender == "Male")$SCkn)

#Communication
CMkn <- data.frame(score = Student3$CMkn,
                   gender = as.factor(Student3$Gender))
ggplot(CMkn, aes(x = gender, y = score, color = gender)) +
  geom_point(position = "jitter", show.legend = FALSE) +
  geom_hline(yintercept = mean(filter(Student2, Gender == "Female")$CMkn), color = "#F8766D") +
  geom_hline(yintercept = mean(filter(Student2, Gender == "Male")$CMkn), color = "#00BFC4") +
  labs(title = "Communication Technology Fluency") +
  theme(plot.title = element_text(hjust = 0.5, size = 20), 
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))

t.test(score ~ gender, data = CMkn)
mean(filter(Student2, Gender == "Female")$CMkn) - mean(filter(Student2, Gender == "Male")$CMkn)

#Meeting
VCkn <- data.frame(score = Student3$VCkn,
                   gender = as.factor(Student3$Gender))
ggplot(VCkn, aes(x = gender, y = score, color = gender)) +
  geom_point(position = "jitter", show.legend = FALSE) +
  geom_hline(yintercept = mean(filter(Student2, Gender == "Female")$VCkn), color = "#F8766D") +
  geom_hline(yintercept = mean(filter(Student2, Gender == "Male")$VCkn), color = "#00BFC4") +
  labs(title = "Meeting Technology Fluency") +
  theme(plot.title = element_text(hjust = 0.5, size = 20), 
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))

t.test(score ~ gender, data = VCkn)
mean(filter(Student2, Gender == "Female")$VCkn) - mean(filter(Student2, Gender == "Male")$VCkn)
```


### Usage

```{r}
#Scheduling
SCus <- data.frame(score = Student3$SCus,
                   gender = as.factor(Student3$Gender))
ggplot(SCus, aes(x = gender, y = score, color = gender)) +
  geom_point(position = "jitter", show.legend = FALSE) +
  geom_hline(yintercept = mean(filter(Student2, Gender == "Female")$SCus), color = "#F8766D") +
  geom_hline(yintercept = mean(filter(Student2, Gender == "Male")$SCus), color = "#00BFC4") +
  labs(title = "Scheduling Technology Usage") +
  theme(plot.title = element_text(hjust = 0.5, size = 20), 
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))

t.test(score ~ gender, data = SCus)
mean(filter(Student2, Gender == "Female")$SCus) - mean(filter(Student2, Gender == "Male")$SCus)

#Communication
CMus <- data.frame(score = Student3$CMus,
                   gender = as.factor(Student3$Gender))
ggplot(CMus, aes(x = gender, y = score, color = gender)) +
  geom_point(position = "jitter", show.legend = FALSE) +
  geom_hline(yintercept = mean(filter(Student2, Gender == "Female")$CMus), color = "#F8766D") +
  geom_hline(yintercept = mean(filter(Student2, Gender == "Male")$CMus), color = "#00BFC4") +
  labs(title = "Communication Technology Usage") +
  theme(plot.title = element_text(hjust = 0.5, size = 20), 
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))

t.test(score ~ gender, data = CMus)
mean(filter(Student2, Gender == "Female")$CMus) - mean(filter(Student2, Gender == "Male")$CMus)

#Meeting
VCus <- data.frame(score = Student3$VCus,
                   gender = as.factor(Student3$Gender))
ggplot(VCus, aes(x = gender, y = score, color = gender)) +
  geom_point(position = "jitter", show.legend = FALSE) +
  geom_hline(yintercept = mean(filter(Student2, Gender == "Female")$VCus), color = "#F8766D") +
  geom_hline(yintercept = mean(filter(Student2, Gender == "Male")$VCus), color = "#00BFC4") +
  labs(title = "Meeting Technology Usage") +
  theme(plot.title = element_text(hjust = 0.5, size = 20), 
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))

t.test(score ~ gender, data = VCus)
mean(filter(Student2, Gender == "Female")$VCus) - mean(filter(Student2, Gender == "Male")$VCus)
```



## Age

### Fluency 

```{r}
mean(Student2$Age)

#Scheduling
cor.test(Student2$SCkn, Student2$Age)
ggplot(Student2, aes(x = Age, y = SCkn, color = Age)) +
  geom_point(position = "jitter", show.legend = FALSE) +
  labs(title = "Scheduling Technology Fluency") +
  theme(plot.title = element_text(hjust = 0.5, size = 20),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))


#Communication
cor.test(Student2$CMkn, Student2$Age)
ggplot(Student2, aes(x = Age, y = CMkn, color = Age)) +
  geom_point(position = "jitter", show.legend = FALSE) +
  labs(title = "Communication Technology Fluency") +
  theme(plot.title = element_text(hjust = 0.5, size = 20),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))

#Meeting
cor.test(Student2$VCkn, Student2$Age)
ggplot(Student2, aes(x = Age, y = VCkn, color = Age)) +
  geom_point(position = "jitter", show.legend = FALSE) +
  labs(title = "Meeting Technology Fluency") +
  theme(plot.title = element_text(hjust = 0.5, size = 20),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))
```


### Usage

```{r}
#Scheduling
cor.test(Student2$SCus, Student2$Age)
ggplot(Student2, aes(x = Age, y = SCus, color = Age)) +
  geom_point(position = "jitter", show.legend = FALSE) +
  labs(title = "Scheduling Technology Usage") +
  theme(plot.title = element_text(hjust = 0.5, size = 20),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))

#Communication
cor.test(Student2$CMus, Student2$Age)
ggplot(Student2, aes(x = Age, y = CMus, color = Age)) +
  geom_point(position = "jitter", show.legend = FALSE) +
  labs(title = "Communication Technology Usage") +
  theme(plot.title = element_text(hjust = 0.5, size = 20),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))

#Meeting
cor.test(Student2$VCus, Student2$Age)
ggplot(Student2, aes(x = Age, y = VCus, color = Age)) +
  geom_point(position = "jitter", show.legend = FALSE) +
  labs(title = "Meeting Technology Usage") +
  theme(plot.title = element_text(hjust = 0.5, size = 20),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))
```


## Class (Year in College)

```{r}
table(Student2$Class)
```


### Fluency

```{r}
#Scheduling
SCkn <- data.frame(score = Student2$SCkn,
                   group = Student2$Class)
ggplot(SCkn, aes(x = group, y = score, color = group)) +
  geom_point(position = "jitter", show.legend = FALSE) +
  geom_hline(yintercept = mean(filter(Student2, Class == "FR")$SCkn), color = "#F8766D") +
  geom_hline(yintercept = mean(filter(Student2, Class == "SO")$SCkn), color = "#00BFC4") +
  geom_hline(yintercept = mean(filter(Student2, Class == "JR")$SCkn), color = "#7CAE00") +
  geom_hline(yintercept = mean(filter(Student2, Class == "SR")$SCkn), color = "#C77CFF") +
  labs(title = "Scheduling Technology Fluency") +
  theme(plot.title = element_text(hjust = 0.5, size = 20), 
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))

meanSCkn <- data.frame(Mean = c(mean(filter(Student2, Class == "FR")$SCkn),
                                mean(filter(Student2, Class == "SO")$SCkn),
                                mean(filter(Student2, Class == "FR")$SCkn),
                                mean(filter(Student2, Class == "SR")$SCkn)),
                       Class = c("FR", "SO", "JR", "SR")) %>%
  arrange(Mean)
meanSCkn
kruskal_test(score ~ group, data = SCkn, distribution = approximate())

#Communication
CMkn <- data.frame(score = Student2$CMkn,
                   group = Student2$Class)
ggplot(CMkn, aes(x = group, y = score, color = group)) +
  geom_point(position = "jitter", show.legend = FALSE) +
  geom_hline(yintercept = mean(filter(Student2, Class == "FR")$CMkn), color = "#F8766D") +
  geom_hline(yintercept = mean(filter(Student2, Class == "SO")$CMkn), color = "#00BFC4") +
  geom_hline(yintercept = mean(filter(Student2, Class == "JR")$CMkn), color = "#7CAE00") +
  geom_hline(yintercept = mean(filter(Student2, Class == "SR")$CMkn), color = "#C77CFF") +
  labs(title = "Communication Technology Fluency") +
  theme(plot.title = element_text(hjust = 0.5, size = 20), 
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))

meanCMkn <- data.frame(Mean = c(mean(filter(Student2, Class == "FR")$CMkn),
                                mean(filter(Student2, Class == "SO")$CMkn),
                                mean(filter(Student2, Class == "FR")$CMkn),
                                mean(filter(Student2, Class == "SR")$CMkn)),
                       Class = c("FR", "SO", "JR", "SR")) %>%
  arrange(Mean)
meanCMkn
kruskal_test(score ~ group, data = CMkn, distribution = approximate())

#Meeting
VCkn <- data.frame(score = Student2$VCkn,
                   group = Student2$Class)
ggplot(VCkn, aes(x = group, y = score, color = group)) +
  geom_point(position = "jitter", show.legend = FALSE) +
  geom_hline(yintercept = mean(filter(Student2, Class == "FR")$VCkn), color = "#F8766D") +
  geom_hline(yintercept = mean(filter(Student2, Class == "SO")$VCkn), color = "#00BFC4") +
  geom_hline(yintercept = mean(filter(Student2, Class == "JR")$VCkn), color = "#7CAE00") +
  geom_hline(yintercept = mean(filter(Student2, Class == "SR")$VCkn), color = "#C77CFF") +
  labs(title = "Meeting Technology Fluency") +
  theme(plot.title = element_text(hjust = 0.5, size = 20), 
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))

meanVCkn <- data.frame(Mean = c(mean(filter(Student2, Class == "FR")$VCkn),
                                mean(filter(Student2, Class == "SO")$VCkn),
                                mean(filter(Student2, Class == "FR")$VCkn),
                                mean(filter(Student2, Class == "SR")$VCkn)),
                       Class = c("FR", "SO", "JR", "SR")) %>%
  arrange(Mean)
meanVCkn
kruskal_test(score ~ group, data = VCkn, distribution = approximate())
```

### Usage

```{r}
#Scheduling
SCus <- data.frame(score = Student2$SCus,
                   group = Student2$Class)
ggplot(SCus, aes(x = group, y = score, color = group)) +
  geom_point(position = "jitter", show.legend = FALSE) +
  geom_hline(yintercept = mean(filter(Student2, Class == "FR")$SCus), color = "#F8766D") +
  geom_hline(yintercept = mean(filter(Student2, Class == "SO")$SCus), color = "#00BFC4") +
  geom_hline(yintercept = mean(filter(Student2, Class == "JR")$SCus), color = "#7CAE00") +
  geom_hline(yintercept = mean(filter(Student2, Class == "SR")$SCus), color = "#C77CFF") +
  labs(title = "Scheduling Technology Usage") +
  theme(plot.title = element_text(hjust = 0.5, size = 20), 
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))

meanSCus <- data.frame(Mean = c(mean(filter(Student2, Class == "FR")$SCus),
                                mean(filter(Student2, Class == "SO")$SCus),
                                mean(filter(Student2, Class == "FR")$SCus),
                                mean(filter(Student2, Class == "SR")$SCus)),
                       Class = c("FR", "SO", "JR", "SR")) %>%
  arrange(Mean)
meanSCus
kruskal_test(score ~ group, data = SCus, distribution = approximate())

#Communication
CMus <- data.frame(score = Student2$CMus,
                   group = Student2$Class)
ggplot(CMus, aes(x = group, y = score, color = group)) +
  geom_point(position = "jitter", show.legend = FALSE) +
  geom_hline(yintercept = mean(filter(Student2, Class == "FR")$CMus), color = "#F8766D") +
  geom_hline(yintercept = mean(filter(Student2, Class == "SO")$CMus), color = "#00BFC4") +
  geom_hline(yintercept = mean(filter(Student2, Class == "JR")$CMus), color = "#7CAE00") +
  geom_hline(yintercept = mean(filter(Student2, Class == "SR")$CMus), color = "#C77CFF") +
  labs(title = "Communication Technology Usage") +
  theme(plot.title = element_text(hjust = 0.5, size = 20), 
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))

meanCMus <- data.frame(Mean = c(mean(filter(Student2, Class == "FR")$CMus),
                                mean(filter(Student2, Class == "SO")$CMus),
                                mean(filter(Student2, Class == "FR")$CMus),
                                mean(filter(Student2, Class == "SR")$CMus)),
                       Class = c("FR", "SO", "JR", "SR")) %>%
  arrange(Mean)
meanCMus
kruskal_test(score ~ group, data = CMus, distribution = approximate())

#Meeting
VCus <- data.frame(score = Student2$VCus,
                   group = Student2$Class)
ggplot(VCus, aes(x = group, y = score, color = group)) +
  geom_point(position = "jitter", show.legend = FALSE) +
  geom_hline(yintercept = mean(filter(Student2, Class == "FR")$VCus), color = "#F8766D") +
  geom_hline(yintercept = mean(filter(Student2, Class == "SO")$VCus), color = "#00BFC4") +
  geom_hline(yintercept = mean(filter(Student2, Class == "JR")$VCus), color = "#7CAE00") +
  geom_hline(yintercept = mean(filter(Student2, Class == "SR")$VCus), color = "#C77CFF") +
  labs(title = "Meeting Technology Usage") +
  theme(plot.title = element_text(hjust = 0.5, size = 20), 
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))

meanVCus <- data.frame(Mean = c(mean(filter(Student2, Class == "FR")$VCus),
                                mean(filter(Student2, Class == "SO")$VCus),
                                mean(filter(Student2, Class == "FR")$VCus),
                                mean(filter(Student2, Class == "SR")$VCus)),
                       Class = c("FR", "SO", "JR", "SR")) %>%
  arrange(Mean)
meanVCus
kruskal_test(score ~ group, data = VCus, distribution = approximate())
```


## College/School

```{r}
table(Student2$`College/School`)

#Since there are only three unknown and one University College, let's remove them for simplicity.
Student3 <- filter(Student2, !(`College/School` %in% c("University College", "Unknown")))

#Recode school names into abbr.
for (i in 1:length(Student3$`College/School`)) {
  if (Student3$`College/School`[i] == "College of Liberal Arts") {Student3$`College/School`[i] <- "CLA"}
  else if (Student3$`College/School`[i] == "College of Science and Engineering") {Student3$`College/School`[i] <- "COSE"}
  else if (Student3$`College/School`[i] == "Herberger Business School") {Student3$`College/School`[i] <- "HBS"}
  else if (Student3$`College/School`[i] == "School of Education") {Student3$`College/School`[i] <- "SOE"}
  else if (Student3$`College/School`[i] == "School of Health and Human Services") {Student3$`College/School`[i] <- "SHHS"}
  else if (Student3$`College/School`[i] == "School of Public Affairs") {Student3$`College/School`[i] <- "SOPA"}
}

```

### Fluency

```{r}
#Scheduling
SCkn <- data.frame(score = Student3$SCkn,
                   group = as.factor(Student3$`College/School`))
ggplot(SCkn, aes(x = group, y = score, color = group)) +
  geom_point(position = "jitter", show.legend = FALSE) +
  geom_hline(yintercept = mean(filter(Student3, `College/School` == "CLA")$SCkn), color = "#F8766D") +
  geom_hline(yintercept = mean(filter(Student3, `College/School` == "COSE")$SCkn), color = "#B79F00") +
  geom_hline(yintercept = mean(filter(Student3, `College/School` == "HBS")$SCkn), color = "#00BA38") +
  geom_hline(yintercept = mean(filter(Student3, `College/School` == "SOE")$SCkn), color = "#00BFC4") +
  geom_hline(yintercept = mean(filter(Student3, `College/School` == "SHHS")$SCkn), color = "#619CFF") +
  geom_hline(yintercept = mean(filter(Student3, `College/School` == "SOPA")$SCkn), color = "#F564E3") +
  labs(title = "Scheduling Technology Fluency") +
  theme(plot.title = element_text(hjust = 0.5, size = 20), 
        axis.title.x = element_blank(), 
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))


meanSCkn <- data.frame(Mean = c(mean(filter(Student3, `College/School` == "CLA")$SCkn),
                                mean(filter(Student3, `College/School` == "COSE")$SCkn),
                                mean(filter(Student3, `College/School` == "HBS")$SCkn),
                                mean(filter(Student3, `College/School` == "SOE")$SCkn),
                                mean(filter(Student3, `College/School` == "SHHS")$SCkn),
                                mean(filter(Student3, `College/School` == "SOPA")$SCkn)),
                       School = c("CLA", "COSE", 
                                  "HBS", "SOE", 
                                  "SHHS", "SOPA")) %>%
  arrange(Mean)
meanSCkn
kruskal_test(score ~ group, data = SCkn, distribution = approximate())


#Communication
CMkn <- data.frame(score = Student3$CMkn,
                   group = as.factor(Student3$`College/School`))
ggplot(CMkn, aes(x = group, y = score, color = group)) +
  geom_point(position = "jitter", show.legend = FALSE) +
  geom_hline(yintercept = mean(filter(Student3, `College/School` == "CLA")$CMkn), color = "#F8766D") +
  geom_hline(yintercept = mean(filter(Student3, `College/School` == "COSE")$CMkn), color = "#B79F00") +
  geom_hline(yintercept = mean(filter(Student3, `College/School` == "HBS")$CMkn), color = "#00BA38") +
  geom_hline(yintercept = mean(filter(Student3, `College/School` == "SOE")$CMkn), color = "#00BFC4") +
  geom_hline(yintercept = mean(filter(Student3, `College/School` == "SHHS")$CMkn), color = "#619CFF") +
  geom_hline(yintercept = mean(filter(Student3, `College/School` == "SOPA")$CMkn), color = "#F564E3") +
  labs(title = "Communication Technology Fluency") +
  theme(plot.title = element_text(hjust = 0.5, size = 20), 
        axis.title.x = element_blank(), 
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))


meanCMkn <- data.frame(Mean = c(mean(filter(Student3, `College/School` == "CLA")$CMkn),
                                mean(filter(Student3, `College/School` == "COSE")$CMkn),
                                mean(filter(Student3, `College/School` == "HBS")$CMkn),
                                mean(filter(Student3, `College/School` == "SOE")$CMkn),
                                mean(filter(Student3, `College/School` == "SHHS")$CMkn),
                                mean(filter(Student3, `College/School` == "SOPA")$CMkn)),
                       School = c("CLA", "COSE", 
                                  "HBS", "SOE", 
                                  "SHHS", "SOPA")) %>%
  arrange(Mean)
meanCMkn
kruskal_test(score ~ group, data = CMkn, distribution = approximate())


#Meeting
VCkn <- data.frame(score = Student3$VCkn,
                   group = as.factor(Student3$`College/School`))
ggplot(VCkn, aes(x = group, y = score, color = group)) +
  geom_point(position = "jitter", show.legend = FALSE) +
  geom_hline(yintercept = mean(filter(Student3, `College/School` == "CLA")$VCkn), color = "#F8766D") +
  geom_hline(yintercept = mean(filter(Student3, `College/School` == "COSE")$VCkn), color = "#B79F00") +
  geom_hline(yintercept = mean(filter(Student3, `College/School` == "HBS")$VCkn), color = "#00BA38") +
  geom_hline(yintercept = mean(filter(Student3, `College/School` == "SOE")$VCkn), color = "#00BFC4") +
  geom_hline(yintercept = mean(filter(Student3, `College/School` == "SHHS")$VCkn), color = "#619CFF") +
  geom_hline(yintercept = mean(filter(Student3, `College/School` == "SOPA")$VCkn), color = "#F564E3") +
  labs(title = "Meeting Technology Fluency") +
  theme(plot.title = element_text(hjust = 0.5, size = 20), 
        axis.title.x = element_blank(), 
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))


meanVCkn <- data.frame(Mean = c(mean(filter(Student3, `College/School` == "CLA")$VCkn),
                                mean(filter(Student3, `College/School` == "COSE")$VCkn),
                                mean(filter(Student3, `College/School` == "HBS")$VCkn),
                                mean(filter(Student3, `College/School` == "SOE")$VCkn),
                                mean(filter(Student3, `College/School` == "SHHS")$VCkn),
                                mean(filter(Student3, `College/School` == "SOPA")$VCkn)),
                       School = c("CLA", "COSE", 
                                  "HBS", "SOE", 
                                  "SHHS", "SOPA")) %>%
  arrange(Mean)
meanVCkn
kruskal_test(score ~ group, data = VCkn, distribution = approximate())
```


### Usage

```{r}
#Scheduling
SCus <- data.frame(score = Student3$SCus,
                   group = as.factor(Student3$`College/School`))
ggplot(SCus, aes(x = group, y = score, color = group)) +
  geom_point(position = "jitter", show.legend = FALSE) +
  geom_hline(yintercept = mean(filter(Student3, `College/School` == "CLA")$SCus), color = "#F8766D") +
  geom_hline(yintercept = mean(filter(Student3, `College/School` == "COSE")$SCus), color = "#B79F00") +
  geom_hline(yintercept = mean(filter(Student3, `College/School` == "HBS")$SCus), color = "#00BA38") +
  geom_hline(yintercept = mean(filter(Student3, `College/School` == "SOE")$SCus), color = "#00BFC4") +
  geom_hline(yintercept = mean(filter(Student3, `College/School` == "SHHS")$SCus), color = "#619CFF") +
  geom_hline(yintercept = mean(filter(Student3, `College/School` == "SOPA")$SCus), color = "#F564E3") +
  labs(title = "Scheduling Technology Usage") +
  theme(plot.title = element_text(hjust = 0.5, size = 20), 
        axis.title.x = element_blank(), 
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))


meanSCus <- data.frame(Mean = c(mean(filter(Student3, `College/School` == "CLA")$SCus),
                                mean(filter(Student3, `College/School` == "COSE")$SCus),
                                mean(filter(Student3, `College/School` == "HBS")$SCus),
                                mean(filter(Student3, `College/School` == "SOE")$SCus),
                                mean(filter(Student3, `College/School` == "SHHS")$SCus),
                                mean(filter(Student3, `College/School` == "SOPA")$SCus)),
                       School = c("CLA", "COSE", 
                                  "HBS", "SOE", 
                                  "SHHS", "SOPA")) %>%
  arrange(Mean)
meanSCus
kruskal_test(score ~ group, data = SCus, distribution = approximate())


#Communication
CMus <- data.frame(score = Student3$CMus,
                   group = as.factor(Student3$`College/School`))
ggplot(CMus, aes(x = group, y = score, color = group)) +
  geom_point(position = "jitter", show.legend = FALSE) +
  geom_hline(yintercept = mean(filter(Student3, `College/School` == "CLA")$CMus), color = "#F8766D") +
  geom_hline(yintercept = mean(filter(Student3, `College/School` == "COSE")$CMus), color = "#B79F00") +
  geom_hline(yintercept = mean(filter(Student3, `College/School` == "HBS")$CMus), color = "#00BA38") +
  geom_hline(yintercept = mean(filter(Student3, `College/School` == "SOE")$CMus), color = "#00BFC4") +
  geom_hline(yintercept = mean(filter(Student3, `College/School` == "SHHS")$CMus), color = "#619CFF") +
  geom_hline(yintercept = mean(filter(Student3, `College/School` == "SOPA")$CMus), color = "#F564E3") +
  labs(title = "Communication Technology Usage") +
  theme(plot.title = element_text(hjust = 0.5, size = 20), 
        axis.title.x = element_blank(), 
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))


meanCMus <- data.frame(Mean = c(mean(filter(Student3, `College/School` == "CLA")$CMus),
                                mean(filter(Student3, `College/School` == "COSE")$CMus),
                                mean(filter(Student3, `College/School` == "HBS")$CMus),
                                mean(filter(Student3, `College/School` == "SOE")$CMus),
                                mean(filter(Student3, `College/School` == "SHHS")$CMus),
                                mean(filter(Student3, `College/School` == "SOPA")$CMus)),
                       School = c("CLA", "COSE", 
                                  "HBS", "SOE", 
                                  "SHHS", "SOPA")) %>%
  arrange(Mean)
meanCMus
kruskal_test(score ~ group, data = CMus, distribution = approximate())


#Meeting
VCus <- data.frame(score = Student3$VCus,
                   group = as.factor(Student3$`College/School`))
ggplot(VCus, aes(x = group, y = score, color = group)) +
  geom_point(position = "jitter", show.legend = FALSE) +
  geom_hline(yintercept = mean(filter(Student3, `College/School` == "CLA")$VCus), color = "#F8766D") +
  geom_hline(yintercept = mean(filter(Student3, `College/School` == "COSE")$VCus), color = "#B79F00") +
  geom_hline(yintercept = mean(filter(Student3, `College/School` == "HBS")$VCus), color = "#00BA38") +
  geom_hline(yintercept = mean(filter(Student3, `College/School` == "SOE")$VCus), color = "#00BFC4") +
  geom_hline(yintercept = mean(filter(Student3, `College/School` == "SHHS")$VCus), color = "#619CFF") +
  geom_hline(yintercept = mean(filter(Student3, `College/School` == "SOPA")$VCus), color = "#F564E3") +
  labs(title = "Meeting Technology Usage") +
  theme(plot.title = element_text(hjust = 0.5, size = 20), 
        axis.title.x = element_blank(), 
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 12))


meanVCus <- data.frame(Mean = c(mean(filter(Student3, `College/School` == "CLA")$VCus),
                                mean(filter(Student3, `College/School` == "COSE")$VCus),
                                mean(filter(Student3, `College/School` == "HBS")$VCus),
                                mean(filter(Student3, `College/School` == "SOE")$VCus),
                                mean(filter(Student3, `College/School` == "SHHS")$VCus),
                                mean(filter(Student3, `College/School` == "SOPA")$VCus)),
                       School = c("CLA", "COSE", 
                                  "HBS", "SOE", 
                                  "SHHS", "SOPA")) %>%
  arrange(Mean)
meanVCus
kruskal_test(score ~ group, data = VCus, distribution = approximate())
```

## Overall Scores

```{r}
Student3 <- Student2 %>% 
  mutate(Fluency = SCkn + CMkn + VCkn,
         Usage = SCus + CMus + VCus)
```


### Simple OLS

```{r}
#Fluency
full <- lm(Fluency ~ Gender + Age + `College/School` + Class + Location, data = Student3)
summary(full)

GenderAge <- lm(Fluency ~ Gender + Age, data = Student3)
summary(GenderAge)

SchoolClass <- lm(Fluency ~ `College/School` + Class, data = Student3)
summary(SchoolClass)

LocationClass <- lm(Fluency ~ Location + Class, data = Student3)
summary(LocationClass)
```

